# Experiment 1 Procedure

 
This arm of the project is the linearity study. In this study three organisms will be used: Staphylococcus aureus, Pseudomonas aeruginosa, Aspergillus brasiliensis at 5 different inoculum levels. This procedure is to be performed over a period of two days.  

**Day 1:**

*	Streak colony from culture plate onto agar slope  
*	Incubate agar slope overnight

**Day 2:**

*	Add glass beads to the inoculated agar slope
* Add 10ml saline to the inoculated slope  
*	Invert the slope a few times 
*	Vortex the slope for 1 minute 
*	Dispense 0.1ml of stock solution in 9.9ml 0.9% saline = 105 
*	Dispense 0.1ml of 105 dilution in 9.9ml of 0.9% saline = 103
*	Dispense 2.0ml of 105 dilution in 8.0ml of 0.9% saline = 500cfu 
*	Dispense 1.0ml of 103 dilution in 9.0ml of 0.9% saline = 102 
*	Dispense 1.0ml of 500cfu dilution in 9.0ml of 0.9% saline = 50cfu 
*	Dispense 1.0ml of 50cfu dilution in 9.0ml of 0.9% saline = 5cfu 
*	Dispense 0.1ml 102 dilution in 9.9ml of 0.9% saline = 1cfu


The dilutions outlined in bold are the ones to be used in this study. 

Streak 0.1ml of selected dilutions onto 10 settle plates and 10 settle plates per dilution and incubate at 30-35°C for 5 days.   

Once the incubation period is complete, the plates will be read by two technicians - without marking with a pen and by both plate readers. 

```{r global_options,error=FALSE,warning=FALSE,fig.width=7,fig.height=7,echo=FALSE}
knitr::opts_chunk$set(error=FALSE,warning=FALSE,fig.width=7,fig.height=5,echo=FALSE,message = FALSE)
```

```{r, include=FALSE}
library(blandr)
library(ggplot2)
library(xlsx)
library(dplyr)
library(tibble)
```

```{r,include=FALSE,resuls="hide"}
setwd("/Users/krpl818/OneDrive - AZCollaboration/Documents/Plate reader project")

library(readxl)
experiment_1 <- read_excel("Experiment tables.xlsx", 
                                col_types = c("text", "text", "numeric", 
                                              "text", "numeric", "numeric"))
experiment_1<-as_tibble(experiment_1)
attach(experiment_1)
names(experiment_1)
```

```{r,results="hide"}

Analyst1_staphaur_settle_1<-filter(experiment_1,experiment_1["Method"]=="First Analyst",experiment_1["Organism"]=='Staphylococcus aureus',experiment_1["Inoculation level"]==1,experiment_1["Plate Type"]=='Settle')

Analyst1_staphaur_settle_10<-filter(experiment_1,experiment_1["Method"]=="First Analyst",experiment_1["Organism"]=='Staphylococcus aureus',experiment_1["Inoculation level"]==10,experiment_1["Plate Type"]=='Settle')

Analyst1_staphaur_settle_50<-filter(experiment_1,experiment_1["Method"]=="First Analyst",experiment_1["Organism"]=='Staphylococcus aureus',experiment_1["Inoculation level"]==50,experiment_1["Plate Type"]=='Settle')

Analyst1_staphaur_settle_100<-filter(experiment_1,experiment_1["Method"]=="First Analyst",experiment_1["Organism"]=='Staphylococcus aureus',experiment_1["Inoculation level"]==100,experiment_1["Plate Type"]=='Settle')

Analyst1_staphaur_settle_300<-filter(experiment_1,experiment_1["Method"]=="First Analyst",experiment_1["Organism"]=='Staphylococcus aureus',experiment_1["Inoculation level"]==300,experiment_1["Plate Type"]=='Settle')

Analyst2_staphaur_settle_1<-filter(experiment_1,experiment_1["Method"]=='Second Analyst',experiment_1["Organism"]=='Staphylococcus aureus',experiment_1["Inoculation level"]==1,experiment_1["Plate Type"]=='Settle')

Analyst2_staphaur_settle_10<-filter(experiment_1,experiment_1["Method"]=='Second Analyst',experiment_1["Organism"]=='Staphylococcus aureus',experiment_1["Inoculation level"]==10,experiment_1["Plate Type"]=='Settle')

Analyst2_staphaur_settle_50<-filter(experiment_1,experiment_1["Method"]=='Second Analyst',experiment_1["Organism"]=='Staphylococcus aureus',experiment_1["Inoculation level"]==50,experiment_1["Plate Type"]=='Settle')

Analyst2_staphaur_settle_100<-filter(experiment_1,experiment_1["Method"]=='Second Analyst',experiment_1["Organism"]=='Staphylococcus aureus',experiment_1["Inoculation level"]==100,experiment_1["Plate Type"]=='Settle')

Analyst2_staphaur_settle_300<-filter(experiment_1,experiment_1["Method"]=='Second Analyst',experiment_1["Organism"]=='Staphylococcus aureus',experiment_1["Inoculation level"]==300,experiment_1["Plate Type"]=='Settle')


Biospot_staphaur_settle_1<-filter(experiment_1,experiment_1["Method"]=='Biospot',experiment_1["Organism"]=='Staphylococcus aureus',experiment_1["Inoculation level"]==1,experiment_1["Plate Type"]=='Settle')

Biospot_staphaur_settle_10<-filter(experiment_1,experiment_1["Method"]=='Biospot',experiment_1["Organism"]=='Staphylococcus aureus',experiment_1["Inoculation level"]==10,experiment_1["Plate Type"]=='Settle')

Biospot_staphaur_settle_50<-filter(experiment_1,experiment_1["Method"]=='Biospot',experiment_1["Organism"]=='Staphylococcus aureus',experiment_1["Inoculation level"]==50,experiment_1["Plate Type"]=='Settle')

Biospot_staphaur_settle_100<-filter(experiment_1,experiment_1["Method"]=='Biospot',experiment_1["Organism"]=='Staphylococcus aureus',experiment_1["Inoculation level"]==100,experiment_1["Plate Type"]=='Settle')

Biospot_staphaur_settle_300<-filter(experiment_1,experiment_1["Method"]=='Biospot',experiment_1["Organism"]=='Staphylococcus aureus',experiment_1["Inoculation level"]==300,experiment_1["Plate Type"]=='Settle')

AutoCol_staphaur_settle_1<-filter(experiment_1,experiment_1["Method"]=='AutoCol',experiment_1["Organism"]=='Staphylococcus aureus',experiment_1["Inoculation level"]==1,experiment_1["Plate Type"]=='Settle')

AutoCol_staphaur_settle_10<-filter(experiment_1,experiment_1["Method"]=='AutoCol',experiment_1["Organism"]=='Staphylococcus aureus',experiment_1["Inoculation level"]==10,experiment_1["Plate Type"]=='Settle')

AutoCol_staphaur_settle_50<-filter(experiment_1,experiment_1["Method"]=='AutoCol',experiment_1["Organism"]=='Staphylococcus aureus',experiment_1["Inoculation level"]==50,experiment_1["Plate Type"]=='Settle')

AutoCol_staphaur_settle_100<-filter(experiment_1,experiment_1["Method"]=='AutoCol',experiment_1["Organism"]=='Staphylococcus aureus',experiment_1["Inoculation level"]==100,experiment_1["Plate Type"]=='Settle')

AutoCol_staphaur_settle_300<-filter(experiment_1,experiment_1["Method"]=='AutoCol',experiment_1["Organism"]=='Staphylococcus aureus',experiment_1["Inoculation level"]==300,experiment_1["Plate Type"]=='Settle')

as.data.frame(Analyst1_staphaur_settle_1)
as.data.frame(Analyst1_staphaur_settle_10)
as.data.frame(Analyst1_staphaur_settle_100)
as.data.frame(Analyst1_staphaur_settle_50)
as.data.frame(Analyst1_staphaur_settle_300)
as.data.frame(Analyst2_staphaur_settle_1)
as.data.frame(Analyst2_staphaur_settle_10)
as.data.frame(Analyst2_staphaur_settle_100)
as.data.frame(Analyst2_staphaur_settle_50)
as.data.frame(Analyst2_staphaur_settle_300)
as.data.frame(Biospot_staphaur_settle_1)
as.data.frame(Biospot_staphaur_settle_10)
as.data.frame(Biospot_staphaur_settle_100)
as.data.frame(Biospot_staphaur_settle_50)
as.data.frame(Biospot_staphaur_settle_300)
as.data.frame(AutoCol_staphaur_settle_1)
as.data.frame(AutoCol_staphaur_settle_10)
as.data.frame(AutoCol_staphaur_settle_100)
as.data.frame(AutoCol_staphaur_settle_50)
as.data.frame(AutoCol_staphaur_settle_300)

Analyst1_Asper_settle_1<-filter(experiment_1,experiment_1["Method"]=="First Analyst",experiment_1["Organism"]=='Aspergillus brasiliensis',experiment_1["Inoculation level"]==1,experiment_1["Plate Type"]=='Settle')

Analyst1_Asper_settle_10<-filter(experiment_1,experiment_1["Method"]=="First Analyst",experiment_1["Organism"]=='Aspergillus brasiliensis',experiment_1["Inoculation level"]==10,experiment_1["Plate Type"]=='Settle')

Analyst1_Asper_settle_50<-filter(experiment_1,experiment_1["Method"]=="First Analyst",experiment_1["Organism"]=='Aspergillus brasiliensis',experiment_1["Inoculation level"]==50,experiment_1["Plate Type"]=='Settle')

Analyst1_Asper_settle_100<-filter(experiment_1,experiment_1["Method"]=="First Analyst",experiment_1["Organism"]=='Aspergillus brasiliensis',experiment_1["Inoculation level"]==100,experiment_1["Plate Type"]=='Settle')

Analyst1_Asper_settle_300<-filter(experiment_1,experiment_1["Method"]=="First Analyst",experiment_1["Organism"]=='Aspergillus brasiliensis',experiment_1["Inoculation level"]==300,experiment_1["Plate Type"]=='Settle')

Analyst2_Asper_settle_1<-filter(experiment_1,experiment_1["Method"]=='Second Analyst',experiment_1["Organism"]=='Aspergillus brasiliensis',experiment_1["Inoculation level"]==1,experiment_1["Plate Type"]=='Settle')

Analyst2_Asper_settle_10<-filter(experiment_1,experiment_1["Method"]=='Second Analyst',experiment_1["Organism"]=='Aspergillus brasiliensis',experiment_1["Inoculation level"]==10,experiment_1["Plate Type"]=='Settle')

Analyst2_Asper_settle_50<-filter(experiment_1,experiment_1["Method"]=='Second Analyst',experiment_1["Organism"]=='Aspergillus brasiliensis',experiment_1["Inoculation level"]==50,experiment_1["Plate Type"]=='Settle')

Analyst2_Asper_settle_100<-filter(experiment_1,experiment_1["Method"]=='Second Analyst',experiment_1["Organism"]=='Aspergillus brasiliensis',experiment_1["Inoculation level"]==100,experiment_1["Plate Type"]=='Settle')

Analyst2_Asper_settle_300<-filter(experiment_1,experiment_1["Method"]=='Second Analyst',experiment_1["Organism"]=='Aspergillus brasiliensis',experiment_1["Inoculation level"]==300,experiment_1["Plate Type"]=='Settle')


Biospot_Asper_settle_1<-filter(experiment_1,experiment_1["Method"]=='Biospot',experiment_1["Organism"]=='Aspergillus brasiliensis',experiment_1["Inoculation level"]==1,experiment_1["Plate Type"]=='Settle')

Biospot_Asper_settle_10<-filter(experiment_1,experiment_1["Method"]=='Biospot',experiment_1["Organism"]=='Aspergillus brasiliensis',experiment_1["Inoculation level"]==10,experiment_1["Plate Type"]=='Settle')

Biospot_Asper_settle_50<-filter(experiment_1,experiment_1["Method"]=='Biospot',experiment_1["Organism"]=='Aspergillus brasiliensis',experiment_1["Inoculation level"]==50,experiment_1["Plate Type"]=='Settle')

Biospot_Asper_settle_100<-filter(experiment_1,experiment_1["Method"]=='Biospot',experiment_1["Organism"]=='Aspergillus brasiliensis',experiment_1["Inoculation level"]==100,experiment_1["Plate Type"]=='Settle')

Biospot_Asper_settle_300<-filter(experiment_1,experiment_1["Method"]=='Biospot',experiment_1["Organism"]=='Aspergillus brasiliensis',experiment_1["Inoculation level"]==300,experiment_1["Plate Type"]=='Settle')

AutoCol_Asper_settle_1<-filter(experiment_1,experiment_1["Method"]=='AutoCol',experiment_1["Organism"]=='Aspergillus brasiliensis',experiment_1["Inoculation level"]==1,experiment_1["Plate Type"]=='Settle')

AutoCol_Asper_settle_10<-filter(experiment_1,experiment_1["Method"]=='AutoCol',experiment_1["Organism"]=='Aspergillus brasiliensis',experiment_1["Inoculation level"]==10,experiment_1["Plate Type"]=='Settle')

AutoCol_Asper_settle_50<-filter(experiment_1,experiment_1["Method"]=='AutoCol',experiment_1["Organism"]=='Aspergillus brasiliensis',experiment_1["Inoculation level"]==50,experiment_1["Plate Type"]=='Settle')

AutoCol_Asper_settle_100<-filter(experiment_1,experiment_1["Method"]=='AutoCol',experiment_1["Organism"]=='Aspergillus brasiliensis',experiment_1["Inoculation level"]==100,experiment_1["Plate Type"]=='Settle')

AutoCol_Asper_settle_300<-filter(experiment_1,experiment_1["Method"]=='AutoCol',experiment_1["Organism"]=='Aspergillus brasiliensis',experiment_1["Inoculation level"]==300,experiment_1["Plate Type"]=='Settle')


as.data.frame(Analyst1_Asper_settle_1)
as.data.frame(Analyst1_Asper_settle_10)
as.data.frame(Analyst1_Asper_settle_100)
as.data.frame(Analyst1_Asper_settle_50)
as.data.frame(Analyst1_Asper_settle_300)
as.data.frame(Analyst2_Asper_settle_1)
as.data.frame(Analyst2_Asper_settle_10)
as.data.frame(Analyst2_Asper_settle_100)
as.data.frame(Analyst2_Asper_settle_50)
as.data.frame(Analyst2_Asper_settle_300)
as.data.frame(Biospot_Asper_settle_1)
as.data.frame(Biospot_Asper_settle_10)
as.data.frame(Biospot_Asper_settle_100)
as.data.frame(Biospot_Asper_settle_50)
as.data.frame(Biospot_Asper_settle_300)
as.data.frame(AutoCol_Asper_settle_1)
as.data.frame(AutoCol_Asper_settle_10)
as.data.frame(AutoCol_Asper_settle_100)
as.data.frame(AutoCol_Asper_settle_50)
as.data.frame(AutoCol_Asper_settle_300)

Analyst1_Pseud_settle_1<-filter(experiment_1,experiment_1["Method"]=="First Analyst",experiment_1["Organism"]=='Pseudomonas aeruginosa',experiment_1["Inoculation level"]==1,experiment_1["Plate Type"]=='Settle')

Analyst1_Pseud_settle_10<-filter(experiment_1,experiment_1["Method"]=="First Analyst",experiment_1["Organism"]=='Pseudomonas aeruginosa',experiment_1["Inoculation level"]==10,experiment_1["Plate Type"]=='Settle')

Analyst1_Pseud_settle_50<-filter(experiment_1,experiment_1["Method"]=="First Analyst",experiment_1["Organism"]=='Pseudomonas aeruginosa',experiment_1["Inoculation level"]==50,experiment_1["Plate Type"]=='Settle')

Analyst1_Pseud_settle_100<-filter(experiment_1,experiment_1["Method"]=="First Analyst",experiment_1["Organism"]=='Pseudomonas aeruginosa',experiment_1["Inoculation level"]==100,experiment_1["Plate Type"]=='Settle')

Analyst1_Pseud_settle_300<-filter(experiment_1,experiment_1["Method"]=="First Analyst",experiment_1["Organism"]=='Pseudomonas aeruginosa',experiment_1["Inoculation level"]==300,experiment_1["Plate Type"]=='Settle')

Analyst2_Pseud_settle_1<-filter(experiment_1,experiment_1["Method"]=='Second Analyst',experiment_1["Organism"]=='Pseudomonas aeruginosa',experiment_1["Inoculation level"]==1,experiment_1["Plate Type"]=='Settle')

Analyst2_Pseud_settle_10<-filter(experiment_1,experiment_1["Method"]=='Second Analyst',experiment_1["Organism"]=='Pseudomonas aeruginosa',experiment_1["Inoculation level"]==10,experiment_1["Plate Type"]=='Settle')

Analyst2_Pseud_settle_50<-filter(experiment_1,experiment_1["Method"]=='Second Analyst',experiment_1["Organism"]=='Pseudomonas aeruginosa',experiment_1["Inoculation level"]==50,experiment_1["Plate Type"]=='Settle')

Analyst2_Pseud_settle_100<-filter(experiment_1,experiment_1["Method"]=='Second Analyst',experiment_1["Organism"]=='Pseudomonas aeruginosa',experiment_1["Inoculation level"]==100,experiment_1["Plate Type"]=='Settle')

Analyst2_Pseud_settle_300<-filter(experiment_1,experiment_1["Method"]=='Second Analyst',experiment_1["Organism"]=='Pseudomonas aeruginosa',experiment_1["Inoculation level"]==300,experiment_1["Plate Type"]=='Settle')


Biospot_Pseud_settle_1<-filter(experiment_1,experiment_1["Method"]=='Biospot',experiment_1["Organism"]=='Pseudomonas aeruginosa',experiment_1["Inoculation level"]==1,experiment_1["Plate Type"]=='Settle')

Biospot_Pseud_settle_10<-filter(experiment_1,experiment_1["Method"]=='Biospot',experiment_1["Organism"]=='Pseudomonas aeruginosa',experiment_1["Inoculation level"]==10,experiment_1["Plate Type"]=='Settle')

Biospot_Pseud_settle_50<-filter(experiment_1,experiment_1["Method"]=='Biospot',experiment_1["Organism"]=='Pseudomonas aeruginosa',experiment_1["Inoculation level"]==50,experiment_1["Plate Type"]=='Settle')

Biospot_Pseud_settle_100<-filter(experiment_1,experiment_1["Method"]=='Biospot',experiment_1["Organism"]=='Pseudomonas aeruginosa',experiment_1["Inoculation level"]==100,experiment_1["Plate Type"]=='Settle')

Biospot_Pseud_settle_300<-filter(experiment_1,experiment_1["Method"]=='Biospot',experiment_1["Organism"]=='Pseudomonas aeruginosa',experiment_1["Inoculation level"]==300,experiment_1["Plate Type"]=='Settle')

AutoCol_Pseud_settle_1<-filter(experiment_1,experiment_1["Method"]=='AutoCol',experiment_1["Organism"]=='Pseudomonas aeruginosa',experiment_1["Inoculation level"]==1,experiment_1["Plate Type"]=='Settle')

AutoCol_Pseud_settle_10<-filter(experiment_1,experiment_1["Method"]=='AutoCol',experiment_1["Organism"]=='Pseudomonas aeruginosa',experiment_1["Inoculation level"]==10,experiment_1["Plate Type"]=='Settle')

AutoCol_Pseud_settle_50<-filter(experiment_1,experiment_1["Method"]=='AutoCol',experiment_1["Organism"]=='Pseudomonas aeruginosa',experiment_1["Inoculation level"]==50,experiment_1["Plate Type"]=='Settle')

AutoCol_Pseud_settle_100<-filter(experiment_1,experiment_1["Method"]=='AutoCol',experiment_1["Organism"]=='Pseudomonas aeruginosa',experiment_1["Inoculation level"]==100,experiment_1["Plate Type"]=='Settle')

AutoCol_Pseud_settle_300<-filter(experiment_1,experiment_1["Method"]=='AutoCol',experiment_1["Organism"]=='Pseudomonas aeruginosa',experiment_1["Inoculation level"]==300,experiment_1["Plate Type"]=='Settle')


as.data.frame(Analyst1_Pseud_settle_1)
as.data.frame(Analyst1_Pseud_settle_10)
as.data.frame(Analyst1_Pseud_settle_100)
as.data.frame(Analyst1_Pseud_settle_50)
as.data.frame(Analyst1_Pseud_settle_300)
as.data.frame(Analyst2_Pseud_settle_1)
as.data.frame(Analyst2_Pseud_settle_10)
as.data.frame(Analyst2_Pseud_settle_100)
as.data.frame(Analyst2_Pseud_settle_50)
as.data.frame(Analyst2_Pseud_settle_300)
as.data.frame(Biospot_Pseud_settle_1)
as.data.frame(Biospot_Pseud_settle_10)
as.data.frame(Biospot_Pseud_settle_100)
as.data.frame(Biospot_Pseud_settle_50)
as.data.frame(Biospot_Pseud_settle_300)
as.data.frame(AutoCol_Pseud_settle_1)
as.data.frame(AutoCol_Pseud_settle_10)
as.data.frame(AutoCol_Pseud_settle_100)
as.data.frame(AutoCol_Pseud_settle_50)
as.data.frame(AutoCol_Pseud_settle_300)
```

```{r, results="hide"}
experiment_1_settle_staph<-filter(experiment_1,experiment_1["Plate Type"]=='Settle',experiment_1["Organism"]=='Staphylococcus aureus')
experiment_1_settle_staph<-as.data.frame(experiment_1_settle_staph)

experiment_1_settle_asper<-filter(experiment_1,experiment_1["Plate Type"]=='Settle',experiment_1["Organism"]=='Aspergillus brasiliensis')
experiment_1_settle_asper<-as.data.frame(experiment_1_settle_asper)

experiment_1_settle_pseud<-filter(experiment_1,experiment_1["Plate Type"]=='Settle',experiment_1["Organism"]=='Pseudomonas aeruginosa')
experiment_1_settle_pseud<-as.data.frame(experiment_1_settle_pseud)

```

```{r,results="hide"}

#staph
A1_A2blandr_1<-blandr.statistics(Analyst1_staphaur_settle_1[[5]],Analyst2_staphaur_settle_1[[5]],sig.level=0.95)

A1_A2blandr_10<-blandr.statistics(Analyst1_staphaur_settle_10[[5]],Analyst2_staphaur_settle_10[[5]],sig.level=0.95)

A1_A2blandr_50<-blandr.statistics(Analyst1_staphaur_settle_50[[5]],Analyst2_staphaur_settle_50[[5]],sig.level=0.95)

A1_A2blandr_100<-blandr.statistics(Analyst1_staphaur_settle_100[[5]],Analyst2_staphaur_settle_100[[5]],sig.level=0.95)

A1_A2blandr_300<-blandr.statistics(Analyst1_staphaur_settle_300[[5]],Analyst2_staphaur_settle_300[[5]],sig.level=0.95)

A1_Biospotblandr_1<-blandr.statistics(Analyst1_staphaur_settle_1[[5]],Biospot_staphaur_settle_1[[5]],sig.level=0.95)

A1_Biospotblandr_10<-blandr.statistics(Analyst1_staphaur_settle_10[[5]],Biospot_staphaur_settle_10[[5]],sig.level=0.95)

A1_Biospotblandr_50<-blandr.statistics(Analyst1_staphaur_settle_50[[5]],Biospot_staphaur_settle_50[[5]],sig.level=0.95)

A1_Biospotblandr_100<-blandr.statistics(Analyst1_staphaur_settle_100[[5]],Biospot_staphaur_settle_100[[5]],sig.level=0.95)

A1_Biospotblandr_300<-blandr.statistics(Analyst1_staphaur_settle_300[[5]],Biospot_staphaur_settle_300[[5]],sig.level=0.95)


A1_AutoColblandr_1<-blandr.statistics(Analyst1_staphaur_settle_1[[5]],AutoCol_staphaur_settle_1[[5]],sig.level=0.95)

A1_AutoColblandr_10<-blandr.statistics(Analyst1_staphaur_settle_10[[5]],AutoCol_staphaur_settle_10[[5]],sig.level=0.95)

A1_AutoColblandr_100<-blandr.statistics(Analyst1_staphaur_settle_100[[5]],AutoCol_staphaur_settle_100[[5]],sig.level=0.95)

A1_AutoColblandr_300<-blandr.statistics(Analyst1_staphaur_settle_300[[5]],AutoCol_staphaur_settle_300[[5]],sig.level=0.95)

A1_AutoColblandr_1<-blandr.statistics(Analyst1_staphaur_settle_1[[5]],AutoCol_staphaur_settle_1[[5]],sig.level=0.95)


A2_Biospotblandr_1<-blandr.statistics(Analyst2_staphaur_settle_1[[5]],Biospot_staphaur_settle_1[[5]],sig.level=0.95)

A2_Biospotblandr_10<-blandr.statistics(Analyst2_staphaur_settle_10[[5]],Biospot_staphaur_settle_10[[5]],sig.level=0.95)

A2_Biospotblandr_50<-blandr.statistics(Analyst2_staphaur_settle_50[[5]],Biospot_staphaur_settle_50[[5]],sig.level=0.95)

A2_Biospotblandr_100<-blandr.statistics(Analyst2_staphaur_settle_100[[5]],Biospot_staphaur_settle_100[[5]],sig.level=0.95)

A2_Biospotblandr_300<-blandr.statistics(Analyst2_staphaur_settle_300[[5]],Biospot_staphaur_settle_300[[5]],sig.level=0.95)


A2_AutoColblandr_1<-blandr.statistics(Analyst2_staphaur_settle_1[[5]],AutoCol_staphaur_settle_1[[5]],sig.level=0.95)

A2_AutoColblandr_10<-blandr.statistics(Analyst2_staphaur_settle_10[[5]],AutoCol_staphaur_settle_10[[5]],sig.level=0.95)

A2_AutoColblandr_50<-blandr.statistics(Analyst2_staphaur_settle_50[[5]],AutoCol_staphaur_settle_50[[5]],sig.level=0.95)

A2_AutoColblandr_100<-blandr.statistics(Analyst2_staphaur_settle_100[[5]],AutoCol_staphaur_settle_100[[5]],sig.level=0.95)

A2_AutoColblandr_300<-blandr.statistics(Analyst2_staphaur_settle_300[[5]],AutoCol_staphaur_settle_300[[5]],sig.level=0.95)


Biospot_AutoColblandr_1<-blandr.statistics(Biospot_staphaur_settle_1[[5]],AutoCol_staphaur_settle_1[[5]],sig.level=0.95)

Biospot_AutoColblandr_10<-blandr.statistics(Biospot_staphaur_settle_10[[5]],AutoCol_staphaur_settle_10[[5]],sig.level=0.95)

Biospot_AutoColblandr_50<-blandr.statistics(Biospot_staphaur_settle_50[[5]],AutoCol_staphaur_settle_50[[5]],sig.level=0.95)

Biospot_AutoColblandr_100<-blandr.statistics(Biospot_staphaur_settle_100[[5]],AutoCol_staphaur_settle_100[[5]],sig.level=0.95)

Biospot_AutoColblandr_300<-blandr.statistics(Biospot_staphaur_settle_300[[5]],AutoCol_staphaur_settle_300[[5]],sig.level=0.95)

```

## Staphylococcus aureus Settle Plates:

```{r, eval=TRUE}
ggplot(data = experiment_1_settle_staph,aes(x=experiment_1_settle_staph$Method, y=experiment_1_settle_staph$`Number of colonies`)) +
  geom_line(aes(group=interaction(experiment_1_settle_staph$`Inoculation level`,experiment_1_settle_staph$Repeat)),color='black')+
  geom_point(aes(x=experiment_1_settle_staph$Method, y=experiment_1_settle_staph$`Number of colonies`,color=experiment_1_settle_staph$Method))+facet_wrap(~experiment_1_settle_staph$`Inoculation level`)+
  labs(y="Number of Colonies counted", x = "Method")+theme(legend.position = "none")
```

**1) Analyst 1 compared to Analyst 2 :**

1 cfu

```{r, eval=TRUE}
A1_A2_sum_stats_staph_1<-blandr.output.text(Analyst1_staphaur_settle_1[[5]],Analyst2_staphaur_settle_1[[5]],sig.level=0.95)
blandr.draw(Analyst1_staphaur_settle_1[[5]],Analyst2_staphaur_settle_1[[5]])
blandr.plot.normality(A1_A2blandr_1)

```

10 cfu

```{r, eval=TRUE}
A1_A2_sum_stats_staph_10<-blandr.output.text(Analyst1_staphaur_settle_10[[5]],Analyst2_staphaur_settle_10[[5]],sig.level=0.95)
blandr.draw(Analyst1_staphaur_settle_10[[5]],Analyst2_staphaur_settle_10[[5]])
blandr.plot.normality(A1_A2blandr_10)

```

50 cfu

```{r, eval=TRUE}
A1_A2_sum_stats_staph_50<-blandr.output.text(Analyst1_staphaur_settle_50[[5]],Analyst2_staphaur_settle_50[[5]],sig.level=0.95)
blandr.draw(Analyst1_staphaur_settle_50[[5]],Analyst1_staphaur_settle_50[[5]])
blandr.plot.normality(A1_A2blandr_10)

```

100 cfu

```{r, eval=TRUE}
A1_A2_sum_stats_staph_100<-blandr.output.text(Analyst1_staphaur_settle_100[[5]],Analyst2_staphaur_settle_100[[5]],sig.level=0.95)
blandr.draw(Analyst1_staphaur_settle_100[[5]],Analyst2_staphaur_settle_100[[5]])
blandr.plot.normality(A1_A2blandr_100)

```

300cfu 

```{r, eval=TRUE}
A1_A2_sum_stats_staph_300<-blandr.output.text(Analyst1_staphaur_settle_300[[5]],Analyst2_staphaur_settle_300[[5]],sig.level=0.95)
blandr.draw(Analyst1_staphaur_settle_300[[5]],Analyst2_staphaur_settle_300[[5]])
blandr.plot.normality(A1_A2blandr_300)
```

**2) Analyst 1 compared to Biospot :**

1 cfu

```{r, eval=TRUE}
A1_Biospot_sum_stats_staph_1<-blandr.output.text(Analyst1_staphaur_settle_1[[5]],Biospot_staphaur_settle_1[[5]],sig.level=0.95)
blandr.draw(Analyst1_staphaur_settle_1[[5]],Biospot_staphaur_settle_1[[5]])
blandr.plot.normality(A1_Biospotblandr_1)

```

10 cfu

```{r, eval=TRUE}
A1_Biospot_sum_stats_staph_10<-blandr.output.text(Analyst1_staphaur_settle_10[[5]],Biospot_staphaur_settle_10[[5]],sig.level=0.95)
blandr.draw(Analyst1_staphaur_settle_10[[5]],Biospot_staphaur_settle_10[[5]])
blandr.plot.normality(A1_Biospotblandr_10)

```

50 cfu

```{r, eval=TRUE}
A1_Biospot_sum_stats_staph_50<-blandr.output.text(Analyst1_staphaur_settle_50[[5]],Biospot_staphaur_settle_50[[5]],sig.level=0.95)
blandr.draw(Analyst1_staphaur_settle_50[[5]],Biospot_staphaur_settle_50[[5]])
blandr.plot.normality(A1_Biospotblandr_10)

```

100 cfu

```{r, eval=TRUE}
A1_Biospot_sum_stats_staph_100<-blandr.output.text(Analyst1_staphaur_settle_100[[5]],Biospot_staphaur_settle_100[[5]],sig.level=0.95)
blandr.draw(Analyst1_staphaur_settle_100[[5]],Biospot_staphaur_settle_100[[5]])
blandr.plot.normality(A1_Biospotblandr_100)

```
 
300cfu 
```{r, eval=TRUE}
A1_Biospot_sum_stats_staph_300<-blandr.output.text(Analyst1_staphaur_settle_300[[5]],Biospot_staphaur_settle_300[[5]],sig.level=0.95)
blandr.draw(Analyst1_staphaur_settle_300[[5]],Biospot_staphaur_settle_300[[5]])
blandr.plot.normality(A1_Biospotblandr_300)

```

**3) Analyst 1 compared to AutoCol :**

1 cfu

```{r, eval=TRUE}
A1_AutoColsum_stats_staph_1<-blandr.output.text(Analyst1_staphaur_settle_1[[5]],AutoCol_staphaur_settle_1[[5]],sig.level=0.95)
blandr.draw(Analyst1_staphaur_settle_1[[5]],AutoCol_staphaur_settle_1[[5]])
blandr.plot.normality(A1_AutoColblandr_1)

```

10 cfu

```{r, eval=TRUE}
A1_AutoColsum_stats_staph_10<-blandr.output.text(Analyst1_staphaur_settle_10[[5]],AutoCol_staphaur_settle_10[[5]],sig.level=0.95)
blandr.draw(Analyst1_staphaur_settle_10[[5]],AutoCol_staphaur_settle_10[[5]])
blandr.plot.normality(A1_AutoColblandr_10)

```

50 cfu

```{r, eval=TRUE}
A1_AutoColsum_stats_staph_50<-blandr.output.text(Analyst1_staphaur_settle_50[[5]],AutoCol_staphaur_settle_50[[5]],sig.level=0.95)
blandr.draw(Analyst1_staphaur_settle_50[[5]],Analyst1_staphaur_settle_50[[5]])
blandr.plot.normality(A1_AutoColblandr_10)

```

100 cfu

```{r, eval=TRUE}
A1_AutoColsum_stats_staph_100<-blandr.output.text(Analyst1_staphaur_settle_100[[5]],AutoCol_staphaur_settle_100[[5]],sig.level=0.95)
blandr.draw(Analyst1_staphaur_settle_100[[5]],AutoCol_staphaur_settle_100[[5]])
blandr.plot.normality(A1_AutoColblandr_100)

```
 
300cfu 

```{r, eval=TRUE}
A1_AutoColsum_stats_staph_300<-blandr.output.text(Analyst1_staphaur_settle_300[[5]],AutoCol_staphaur_settle_300[[5]],sig.level=0.95)
blandr.draw(Analyst1_staphaur_settle_300[[5]],AutoCol_staphaur_settle_300[[5]])
blandr.plot.normality(A1_AutoColblandr_300)

```

**4) Analyst 2 compared to Biospot:**


1 cfu

```{r, eval=TRUE}
A2_Biospot_sum_stats_staph_1<-blandr.output.text(Analyst2_staphaur_settle_1[[5]],Biospot_staphaur_settle_1[[5]],sig.level=0.95)
blandr.draw(Analyst2_staphaur_settle_1[[5]],Biospot_staphaur_settle_1[[5]])
blandr.plot.normality(A2_Biospotblandr_1)

```

10 cfu

```{r, eval=TRUE}
A2_Biospot_sum_stats_staph_10<-blandr.output.text(Analyst2_staphaur_settle_10[[5]],Biospot_staphaur_settle_10[[5]],sig.level=0.95)
blandr.draw(Analyst2_staphaur_settle_10[[5]],Biospot_staphaur_settle_10[[5]])
blandr.plot.normality(A2_Biospotblandr_10)

```

50 cfu

```{r, eval=TRUE}
A2_Biospot_sum_stats_staph_50<-blandr.output.text(Analyst2_staphaur_settle_50[[5]],Biospot_staphaur_settle_50[[5]],sig.level=0.95)
blandr.draw(Analyst2_staphaur_settle_50[[5]],Biospot_staphaur_settle_50[[5]])
blandr.plot.normality(A2_Biospotblandr_10)

```

100 cfu

```{r, eval=TRUE}
A2_Biospot_sum_stats_staph_100<-blandr.output.text(Analyst2_staphaur_settle_100[[5]],Biospot_staphaur_settle_100[[5]],sig.level=0.95)
blandr.draw(Analyst2_staphaur_settle_100[[5]],Biospot_staphaur_settle_100[[5]])
blandr.plot.normality(A2_Biospotblandr_100)

```
 
300cfu 

```{r, eval=TRUE}
A2_Biospot_sum_stats_staph_300<-blandr.output.text(Analyst2_staphaur_settle_300[[5]],Biospot_staphaur_settle_300[[5]],sig.level=0.95)
blandr.draw(Analyst2_staphaur_settle_300[[5]],Biospot_staphaur_settle_300[[5]])
blandr.plot.normality(A2_Biospotblandr_300)

```

**5) Analyst 2 compared to AutoCol**

1 cfu

```{r, eval=TRUE}
A2_AutoColsum_stats_staph_1<-blandr.output.text(Analyst2_staphaur_settle_1[[5]],AutoCol_staphaur_settle_1[[5]],sig.level=0.95)
blandr.draw(Analyst2_staphaur_settle_1[[5]],AutoCol_staphaur_settle_1[[5]])
blandr.plot.normality(A2_AutoColblandr_1)

```

10 cfu

```{r, eval=TRUE}
A2_AutoColsum_stats_staph_10<-blandr.output.text(Analyst2_staphaur_settle_10[[5]],AutoCol_staphaur_settle_10[[5]],sig.level=0.95)
blandr.draw(Analyst2_staphaur_settle_10[[5]],AutoCol_staphaur_settle_10[[5]])
blandr.plot.normality(A2_AutoColblandr_10)

```

50 cfu

```{r, eval=TRUE}
A2_AutoColsum_stats_staph_50<-blandr.output.text(Analyst2_staphaur_settle_50[[5]],AutoCol_staphaur_settle_50[[5]],sig.level=0.95)
blandr.draw(Analyst2_staphaur_settle_50[[5]],Analyst1_staphaur_settle_50[[5]])
blandr.plot.normality(A2_AutoColblandr_10)

```

100 cfu

```{r, eval=TRUE}
A2_AutoColsum_stats_staph_100<-blandr.output.text(Analyst2_staphaur_settle_100[[5]],AutoCol_staphaur_settle_100[[5]],sig.level=0.95)
blandr.draw(Analyst2_staphaur_settle_100[[5]],AutoCol_staphaur_settle_100[[5]])
blandr.plot.normality(A2_AutoColblandr_100)

```
 
300cfu 

```{r, eval=TRUE}
A2_AutoColsum_stats_staph_300<-blandr.output.text(Analyst2_staphaur_settle_300[[5]],AutoCol_staphaur_settle_300[[5]],sig.level=0.95)
blandr.draw(Analyst2_staphaur_settle_300[[5]],AutoCol_staphaur_settle_300[[5]])
blandr.plot.normality(A2_AutoColblandr_300)
```

**6) Biospot compared to AutoCol :**

1 cfu 

```{r, eval=TRUE}
Biospot_AutoColsum_stats_staph_1<-blandr.output.text(Biospot_staphaur_settle_1[[5]],AutoCol_staphaur_settle_1[[5]],sig.level=0.95)
blandr.draw(Biospot_staphaur_settle_1[[5]],AutoCol_staphaur_settle_1[[5]])
blandr.plot.normality(Biospot_AutoColblandr_1)

```

10 cfu

```{r, eval=TRUE}
Biospot_AutoColsum_stats_staph_10<-blandr.output.text(Biospot_staphaur_settle_10[[5]],AutoCol_staphaur_settle_10[[5]],sig.level=0.95)
blandr.draw(Biospot_staphaur_settle_10[[5]],AutoCol_staphaur_settle_10[[5]])
blandr.plot.normality(Biospot_AutoColblandr_10)

```

50 cfu

```{r, eval=TRUE}
Biospot_AutoColsum_stats_staph_50<-blandr.output.text(Biospot_staphaur_settle_50[[5]],AutoCol_staphaur_settle_50[[5]],sig.level=0.95)
blandr.draw(Biospot_staphaur_settle_50[[5]],Analyst1_staphaur_settle_50[[5]])
blandr.plot.normality(Biospot_AutoColblandr_10)

```

100 cfu

```{r, eval=TRUE}
Biospot_AutoColsum_stats_staph_100<-blandr.output.text(Biospot_staphaur_settle_100[[5]],AutoCol_staphaur_settle_100[[5]],sig.level=0.95)
blandr.draw(Biospot_staphaur_settle_100[[5]],AutoCol_staphaur_settle_100[[5]])
blandr.plot.normality(Biospot_AutoColblandr_100)

```

300cfu 

```{r, eval=TRUE}
Biospot_AutoColsum_stats_staph_300<-blandr.output.text(Biospot_staphaur_settle_300[[5]],AutoCol_staphaur_settle_300[[5]],sig.level=0.95)
blandr.draw(Biospot_staphaur_settle_300[[5]],AutoCol_staphaur_settle_300[[5]])
blandr.plot.normality(Biospot_AutoColblandr_300)
```

```{r,results="hide"}
#Asper

A1_A2blandr_1<-blandr.statistics(Analyst1_Asper_settle_1[[5]],Analyst2_Asper_settle_1[[5]],sig.level=0.95)

A1_A2blandr_10<-blandr.statistics(Analyst1_Asper_settle_10[[5]],Analyst2_Asper_settle_10[[5]],sig.level=0.95)

A1_A2blandr_50<-blandr.statistics(Analyst1_Asper_settle_50[[5]],Analyst2_Asper_settle_50[[5]],sig.level=0.95)

A1_A2blandr_100<-blandr.statistics(Analyst1_Asper_settle_100[[5]],Analyst2_Asper_settle_100[[5]],sig.level=0.95)

A1_A2blandr_300<-blandr.statistics(Analyst1_Asper_settle_300[[5]],Analyst2_Asper_settle_300[[5]],sig.level=0.95)

A1_Biospotblandr_1<-blandr.statistics(Analyst1_Asper_settle_1[[5]],Biospot_Asper_settle_1[[5]],sig.level=0.95)

A1_Biospotblandr_10<-blandr.statistics(Analyst1_Asper_settle_10[[5]],Biospot_Asper_settle_10[[5]],sig.level=0.95)

A1_Biospotblandr_50<-blandr.statistics(Analyst1_Asper_settle_50[[5]],Biospot_Asper_settle_50[[5]],sig.level=0.95)

A1_Biospotblandr_100<-blandr.statistics(Analyst1_Asper_settle_100[[5]],Biospot_Asper_settle_100[[5]],sig.level=0.95)




A1_AutoColblandr_1<-blandr.statistics(Analyst1_Asper_settle_1[[5]],AutoCol_Asper_settle_1[[5]],sig.level=0.95)

A1_AutoColblandr_10<-blandr.statistics(Analyst1_Asper_settle_10[[5]],AutoCol_Asper_settle_10[[5]],sig.level=0.95)

A1_AutoColblandr_100<-blandr.statistics(Analyst1_Asper_settle_100[[5]],AutoCol_Asper_settle_100[[5]],sig.level=0.95)

A1_AutoColblandr_300<-blandr.statistics(Analyst1_Asper_settle_300[[5]],AutoCol_Asper_settle_300[[5]],sig.level=0.95)

A1_AutoColblandr_1<-blandr.statistics(Analyst1_Asper_settle_1[[5]],AutoCol_Asper_settle_1[[5]],sig.level=0.95)


A2_Biospotblandr_1<-blandr.statistics(Analyst2_Asper_settle_1[[5]],Biospot_Asper_settle_1[[5]],sig.level=0.95)

A2_Biospotblandr_10<-blandr.statistics(Analyst2_Asper_settle_10[[5]],Biospot_Asper_settle_10[[5]],sig.level=0.95)

A2_Biospotblandr_50<-blandr.statistics(Analyst2_Asper_settle_50[[5]],Biospot_Asper_settle_50[[5]],sig.level=0.95)

A2_Biospotblandr_100<-blandr.statistics(Analyst2_Asper_settle_100[[5]],Biospot_Asper_settle_100[[5]],sig.level=0.95)


A2_AutoColblandr_1<-blandr.statistics(Analyst2_staphaur_settle_1[[5]],AutoCol_staphaur_settle_1[[5]],sig.level=0.95)

A2_AutoColblandr_10<-blandr.statistics(Analyst2_staphaur_settle_10[[5]],AutoCol_staphaur_settle_10[[5]],sig.level=0.95)

A2_AutoColblandr_50<-blandr.statistics(Analyst2_staphaur_settle_50[[5]],AutoCol_staphaur_settle_50[[5]],sig.level=0.95)

A2_AutoColblandr_100<-blandr.statistics(Analyst2_staphaur_settle_100[[5]],AutoCol_staphaur_settle_100[[5]],sig.level=0.95)

A2_AutoColblandr_300<-blandr.statistics(Analyst2_staphaur_settle_300[[5]],AutoCol_staphaur_settle_300[[5]],sig.level=0.95)


Biospot_AutoColblandr_1<-blandr.statistics(Biospot_Asper_settle_1[[5]],AutoCol_Asper_settle_1[[5]],sig.level=0.95)

Biospot_AutoColblandr_10<-blandr.statistics(Biospot_Asper_settle_10[[5]],AutoCol_Asper_settle_10[[5]],sig.level=0.95)

Biospot_AutoColblandr_50<-blandr.statistics(Biospot_Asper_settle_50[[5]],AutoCol_Asper_settle_50[[5]],sig.level=0.95)

Biospot_AutoColblandr_100<-blandr.statistics(Biospot_Asper_settle_100[[5]],AutoCol_Asper_settle_100[[5]],sig.level=0.95)
```

**1) Analyst 1 compared to Analyst 2:**

1 cfu

```{r, eval=TRUE}
A1_A2_sum_stats_asper_1<-blandr.output.text(Analyst1_Asper_settle_1[[5]],Analyst2_Asper_settle_1[[5]],sig.level=0.95)
blandr.draw(Analyst1_Asper_settle_1[[5]],Analyst2_Asper_settle_1[[5]])
blandr.plot.normality(A1_A2blandr_1)

```

10 cfu

```{r, eval=TRUE}
A1_A2_sum_stats_asper_10<-blandr.output.text(Analyst1_Asper_settle_10[[5]],Analyst2_Asper_settle_10[[5]],sig.level=0.95)
blandr.draw(Analyst1_Asper_settle_10[[5]],Analyst2_Asper_settle_10[[5]])
blandr.plot.normality(A1_A2blandr_10)

```

50 cfu

```{r, eval=TRUE}
A1_A2_sum_stats_asper_50<-blandr.output.text(Analyst1_Asper_settle_50[[5]],Analyst2_Asper_settle_50[[5]],sig.level=0.95)
blandr.draw(Analyst1_Asper_settle_50[[5]],Analyst1_Asper_settle_50[[5]])
blandr.plot.normality(A1_A2blandr_10)

```

100 cfu

```{r, eval=TRUE}
A1_A2_sum_stats_asper_100<-blandr.output.text(Analyst1_Asper_settle_100[[5]],Analyst2_Asper_settle_100[[5]],sig.level=0.95)
blandr.draw(Analyst1_Asper_settle_100[[5]],Analyst2_Asper_settle_100[[5]])
blandr.plot.normality(A1_A2blandr_100)

```
 
300cfu 

```{r, eval=TRUE}
A1_A2_sum_stats_asper_300<-blandr.output.text(Analyst1_Asper_settle_300[[5]],Analyst2_Asper_settle_300[[5]],sig.level=0.95)
blandr.draw(Analyst1_Asper_settle_300[[5]],Analyst2_Asper_settle_300[[5]])
blandr.plot.normality(A1_A2blandr_300)
```

**2) Analyst 1 compared to Biospot:**

1 cfu

```{r, eval=TRUE}
A1_Biospot_sum_stats_asper_1<-blandr.output.text(Analyst1_Asper_settle_1[[5]],Biospot_Asper_settle_1[[5]],sig.level=0.95)
blandr.draw(Analyst1_Asper_settle_1[[5]],Biospot_Asper_settle_1[[5]])
blandr.plot.normality(A1_Biospotblandr_1)

```

10 cfu

```{r, eval=TRUE}
A1_Biospot_sum_stats_asper_10<-blandr.output.text(Analyst1_Asper_settle_10[[5]],Biospot_Asper_settle_10[[5]],sig.level=0.95)
blandr.draw(Analyst1_Asper_settle_10[[5]],Biospot_Asper_settle_10[[5]])
blandr.plot.normality(A1_Biospotblandr_10)

```

50 cfu

```{r, eval=TRUE}
A1_Biospot_sum_stats_asper_50<-blandr.output.text(Analyst1_Asper_settle_50[[5]],Biospot_Asper_settle_50[[5]],sig.level=0.95)
blandr.draw(Analyst1_Asper_settle_50[[5]],Biospot_Asper_settle_50[[5]])
blandr.plot.normality(A1_Biospotblandr_10)

```

100 cfu

```{r, eval=TRUE}
A1_Biospot_sum_stats_asper_100<-blandr.output.text(Analyst1_Asper_settle_100[[5]],Biospot_Asper_settle_100[[5]],sig.level=0.95)
blandr.draw(Analyst1_Asper_settle_100[[5]],Biospot_Asper_settle_100[[5]])
blandr.plot.normality(A1_Biospotblandr_100)

```

300 cfu

Biospot failed TNTC
 
**3) Analyst 1 compared to AutoCol:**

1 cfu

```{r, eval=TRUE}
A1_AutoColsum_stats_asper_1<-blandr.output.text(Analyst1_Asper_settle_1[[5]],AutoCol_Asper_settle_1[[5]],sig.level=0.95)
blandr.draw(Analyst1_Asper_settle_1[[5]],AutoCol_Asper_settle_1[[5]])
blandr.plot.normality(A1_AutoColblandr_1)

```

10 cfu

```{r, eval=TRUE}
A1_AutoColsum_stats_asper_10<-blandr.output.text(Analyst1_Asper_settle_10[[5]],AutoCol_Asper_settle_10[[5]],sig.level=0.95)
blandr.draw(Analyst1_Asper_settle_10[[5]],AutoCol_Asper_settle_10[[5]])
blandr.plot.normality(A1_AutoColblandr_10)

```

50 cfu

```{r, eval=TRUE}
A1_AutoColsum_stats_asper_50<-blandr.output.text(Analyst1_Asper_settle_50[[5]],AutoCol_Asper_settle_50[[5]],sig.level=0.95)
blandr.draw(Analyst1_Asper_settle_50[[5]],Analyst1_Asper_settle_50[[5]])
blandr.plot.normality(A1_AutoColblandr_10)

```

100 cfu

```{r, eval=TRUE}
A1_AutoColsum_stats_asper_100<-blandr.output.text(Analyst1_Asper_settle_100[[5]],AutoCol_Asper_settle_100[[5]],sig.level=0.95)
blandr.draw(Analyst1_Asper_settle_100[[5]],AutoCol_Asper_settle_100[[5]])
blandr.plot.normality(A1_AutoColblandr_100)

```

300 cfu

```{r, eval=TRUE}
A1_AutoColsum_stats_asper_300<-blandr.output.text(Analyst1_Asper_settle_300[[5]],AutoCol_Asper_settle_300[[5]],sig.level=0.95)
blandr.draw(Analyst1_Asper_settle_300[[5]],AutoCol_Asper_settle_300[[5]])
blandr.plot.normality(A1_AutoColblandr_300)

```
 
**4) Analyst 2 compared to Biospot:**

1 cfu

```{r, eval=TRUE}
A2_Biospot_sum_stats_asper_1<-blandr.output.text(Analyst2_Asper_settle_1[[5]],Biospot_Asper_settle_1[[5]],sig.level=0.95)
blandr.draw(Analyst2_Asper_settle_1[[5]],Biospot_Asper_settle_1[[5]])
blandr.plot.normality(A2_Biospotblandr_1)

```

10 cfu

```{r, eval=TRUE}
A2_Biospot_sum_stats_asper_10<-blandr.output.text(Analyst2_Asper_settle_10[[5]],Biospot_Asper_settle_10[[5]],sig.level=0.95)
blandr.draw(Analyst2_Asper_settle_10[[5]],Biospot_Asper_settle_10[[5]])
blandr.plot.normality(A2_Biospotblandr_10)

```

50 cfu

```{r, eval=TRUE}
A2_Biospot_sum_stats_asper_50<-blandr.output.text(Analyst2_Asper_settle_50[[5]],Biospot_Asper_settle_50[[5]],sig.level=0.95)
blandr.draw(Analyst2_Asper_settle_50[[5]],Biospot_Asper_settle_50[[5]])
blandr.plot.normality(A2_Biospotblandr_10)

```

100 cfu

```{r, eval=TRUE}
A2_Biospot_sum_stats_asper_100<-blandr.output.text(Analyst2_Asper_settle_100[[5]],Biospot_Asper_settle_100[[5]],sig.level=0.95)
blandr.draw(Analyst2_Asper_settle_100[[5]],Biospot_Asper_settle_100[[5]])
blandr.plot.normality(A2_Biospotblandr_100)

```

300 cfu

Biospot results failed TNTC



**5) Analyst 2 compared to AutoCol:**

1 cfu

```{r, eval=TRUE}
A2_AutoColsum_stats_asper_1<-blandr.output.text(Analyst2_Asper_settle_1[[5]],AutoCol_Asper_settle_1[[5]],sig.level=0.95)
blandr.draw(Analyst2_Asper_settle_1[[5]],AutoCol_Asper_settle_1[[5]])
blandr.plot.normality(A2_AutoColblandr_1)

```

10 cfu

```{r, eval=TRUE}
A2_AutoColsum_stats_asper_10<-blandr.output.text(Analyst2_Asper_settle_10[[5]],AutoCol_Asper_settle_10[[5]],sig.level=0.95)
blandr.draw(Analyst2_Asper_settle_10[[5]],AutoCol_Asper_settle_10[[5]])
blandr.plot.normality(A2_AutoColblandr_10)

```

50 cfu

```{r, eval=TRUE}
A2_AutoColsum_stats_asper_50<-blandr.output.text(Analyst2_Asper_settle_50[[5]],AutoCol_Asper_settle_50[[5]],sig.level=0.95)
blandr.draw(Analyst2_Asper_settle_50[[5]],Analyst1_Asper_settle_50[[5]])
blandr.plot.normality(A2_AutoColblandr_10)

```

100 cfu

```{r, eval=TRUE}
A2_AutoColsum_stats_asper_100<-blandr.output.text(Analyst2_Asper_settle_100[[5]],AutoCol_Asper_settle_100[[5]],sig.level=0.95)
blandr.draw(Analyst2_Asper_settle_100[[5]],AutoCol_Asper_settle_100[[5]])
blandr.plot.normality(A2_AutoColblandr_100)

```
 
300 cfu

```{r, eval=TRUE}
A2_AutoColsum_stats_asper_300<-blandr.output.text(Analyst2_Asper_settle_300[[5]],AutoCol_Asper_settle_300[[5]],sig.level=0.95)
blandr.draw(Analyst2_Asper_settle_300[[5]],AutoCol_Asper_settle_300[[5]])
blandr.plot.normality(A2_AutoColblandr_300)
```

**6) Biospot compared to AutoCol:**

1 cfu

```{r, eval=TRUE}
Biospot_AutoColsum_stats_asper_1<-blandr.output.text(Biospot_Asper_settle_1[[5]],AutoCol_Asper_settle_1[[5]],sig.level=0.95)
blandr.draw(Biospot_Asper_settle_1[[5]],AutoCol_Asper_settle_1[[5]])
blandr.plot.normality(Biospot_AutoColblandr_1)

```

10 cfu

```{r, eval=TRUE}
Biospot_AutoColsum_stats_asper_10<-blandr.output.text(Biospot_Asper_settle_10[[5]],AutoCol_Asper_settle_10[[5]],sig.level=0.95)
blandr.draw(Biospot_Asper_settle_10[[5]],AutoCol_Asper_settle_10[[5]])
blandr.plot.normality(Biospot_AutoColblandr_10)

```

50 cfu

```{r, eval=TRUE}
Biospot_AutoColsum_stats_asper_50<-blandr.output.text(Biospot_Asper_settle_50[[5]],AutoCol_Asper_settle_50[[5]],sig.level=0.95)
blandr.draw(Biospot_Asper_settle_50[[5]],Analyst1_Asper_settle_50[[5]])
blandr.plot.normality(Biospot_AutoColblandr_10)

```

100 cfu

```{r, eval=TRUE}
Biospot_AutoColsum_stats_asper_100<-blandr.output.text(Biospot_Asper_settle_100[[5]],AutoCol_Asper_settle_100[[5]],sig.level=0.95)
blandr.draw(Biospot_Asper_settle_100[[5]],AutoCol_Asper_settle_100[[5]])
blandr.plot.normality(Biospot_AutoColblandr_100)

```

300 cfu

Biospot failed TNTC

```{r,results="hide"}
# Pseud 
A1_A2blandr_1<-blandr.statistics(Analyst1_Pseud_settle_1[[5]],Analyst2_Pseud_settle_1[[5]],sig.level=0.95)

A1_A2blandr_10<-blandr.statistics(Analyst1_Pseud_settle_10[[5]],Analyst2_Pseud_settle_10[[5]],sig.level=0.95)

A1_A2blandr_50<-blandr.statistics(Analyst1_Pseud_settle_50[[5]],Analyst2_Pseud_settle_50[[5]],sig.level=0.95)

A1_A2blandr_100<-blandr.statistics(Analyst1_Pseud_settle_100[[5]],Analyst2_Pseud_settle_100[[5]],sig.level=0.95)

A1_A2blandr_300<-blandr.statistics(Analyst1_Pseud_settle_300[[5]],Analyst2_Pseud_settle_300[[5]],sig.level=0.95)

A1_Biospotblandr_1<-blandr.statistics(Analyst1_Pseud_settle_1[[5]],Biospot_Pseud_settle_1[[5]],sig.level=0.95)

A1_Biospotblandr_10<-blandr.statistics(Analyst1_Pseud_settle_10[[5]],Biospot_Pseud_settle_10[[5]],sig.level=0.95)

A1_Biospotblandr_50<-blandr.statistics(Analyst1_Pseud_settle_50[[5]],Biospot_Pseud_settle_50[[5]],sig.level=0.95)

A1_Biospotblandr_100<-blandr.statistics(Analyst1_Pseud_settle_100[[5]],Biospot_Pseud_settle_100[[5]],sig.level=0.95)

A1_Biospotblandr_300<-blandr.statistics(Analyst1_Pseud_settle_300[[5]],Biospot_Pseud_settle_300[[5]],sig.level=0.95)


A1_AutoColblandr_1<-blandr.statistics(Analyst1_Pseud_settle_1[[5]],AutoCol_Pseud_settle_1[[5]],sig.level=0.95)

A1_AutoColblandr_10<-blandr.statistics(Analyst1_Pseud_settle_10[[5]],AutoCol_Pseud_settle_10[[5]],sig.level=0.95)

A1_AutoColblandr_100<-blandr.statistics(Analyst1_Pseud_settle_100[[5]],AutoCol_Pseud_settle_100[[5]],sig.level=0.95)

A1_AutoColblandr_300<-blandr.statistics(Analyst1_Pseud_settle_300[[5]],AutoCol_Pseud_settle_300[[5]],sig.level=0.95)

A1_AutoColblandr_1<-blandr.statistics(Analyst1_Pseud_settle_1[[5]],AutoCol_Pseud_settle_1[[5]],sig.level=0.95)


A2_Biospotblandr_1<-blandr.statistics(Analyst2_Pseud_settle_1[[5]],Biospot_Pseud_settle_1[[5]],sig.level=0.95)

A2_Biospotblandr_10<-blandr.statistics(Analyst2_Pseud_settle_10[[5]],Biospot_Pseud_settle_10[[5]],sig.level=0.95)

A2_Biospotblandr_50<-blandr.statistics(Analyst2_Pseud_settle_50[[5]],Biospot_Pseud_settle_50[[5]],sig.level=0.95)

A2_Biospotblandr_100<-blandr.statistics(Analyst2_Pseud_settle_100[[5]],Biospot_Pseud_settle_100[[5]],sig.level=0.95)

A2_Biospotblandr_300<-blandr.statistics(Analyst2_Pseud_settle_300[[5]],Biospot_Pseud_settle_300[[5]],sig.level=0.95)


A2_AutoColblandr_1<-blandr.statistics(Analyst2_staphaur_settle_1[[5]],AutoCol_staphaur_settle_1[[5]],sig.level=0.95)

A2_AutoColblandr_10<-blandr.statistics(Analyst2_staphaur_settle_10[[5]],AutoCol_staphaur_settle_10[[5]],sig.level=0.95)

A2_AutoColblandr_50<-blandr.statistics(Analyst2_staphaur_settle_50[[5]],AutoCol_staphaur_settle_50[[5]],sig.level=0.95)

A2_AutoColblandr_100<-blandr.statistics(Analyst2_staphaur_settle_100[[5]],AutoCol_staphaur_settle_100[[5]],sig.level=0.95)

A2_AutoColblandr_300<-blandr.statistics(Analyst2_staphaur_settle_300[[5]],AutoCol_staphaur_settle_300[[5]],sig.level=0.95)


Biospot_AutoColblandr_1<-blandr.statistics(Biospot_Pseud_settle_1[[5]],AutoCol_Pseud_settle_1[[5]],sig.level=0.95)

Biospot_AutoColblandr_10<-blandr.statistics(Biospot_Pseud_settle_10[[5]],AutoCol_Pseud_settle_10[[5]],sig.level=0.95)

Biospot_AutoColblandr_50<-blandr.statistics(Biospot_Pseud_settle_50[[5]],AutoCol_Pseud_settle_50[[5]],sig.level=0.95)

Biospot_AutoColblandr_100<-blandr.statistics(Biospot_Pseud_settle_100[[5]],AutoCol_Pseud_settle_100[[5]],sig.level=0.95)

Biospot_AutoColblandr_300<-blandr.statistics(Biospot_Pseud_settle_300[[5]],AutoCol_Pseud_settle_300[[5]],sig.level=0.95)
```
## Experiment 1- Pseudomonas aeruginosa

**Method comparison: Analysis of Pseudomonas aeruginosa settle Plates**

**1) Analyst 1 compared to Analyst 2:**

1 cfu

```{r, eval=TRUE}
A1_A2_sum_stats_Pseud_1<-blandr.output.text(Analyst1_Pseud_settle_1[[5]],Analyst2_Pseud_settle_1[[5]],sig.level=0.95)
blandr.draw(Analyst1_Pseud_settle_1[[5]],Analyst2_Pseud_settle_1[[5]])
blandr.plot.normality(A1_A2blandr_1)

```

10 cfu

```{r, eval=TRUE}
A1_A2_sum_stats_Pseud_10<-blandr.output.text(Analyst1_Pseud_settle_10[[5]],Analyst2_Pseud_settle_10[[5]],sig.level=0.95)
blandr.draw(Analyst1_Pseud_settle_10[[5]],Analyst2_Pseud_settle_10[[5]])
blandr.plot.normality(A1_A2blandr_10)

```

50 cfu

```{r, eval=TRUE}
A1_A2_sum_stats_Pseud_50<-blandr.output.text(Analyst1_Pseud_settle_50[[5]],Analyst2_Pseud_settle_50[[5]],sig.level=0.95)
blandr.draw(Analyst1_Pseud_settle_50[[5]],Analyst1_Pseud_settle_50[[5]])
blandr.plot.normality(A1_A2blandr_10)

```

100 cfu

```{r, eval=TRUE}
A1_A2_sum_stats_Pseud_100<-blandr.output.text(Analyst1_Pseud_settle_100[[5]],Analyst2_Pseud_settle_100[[5]],sig.level=0.95)
blandr.draw(Analyst1_Pseud_settle_100[[5]],Analyst2_Pseud_settle_100[[5]])
blandr.plot.normality(A1_A2blandr_100)

```
 
300 cfu 

```{r, eval=TRUE}
A1_A2_sum_stats_Pseud_300<-blandr.output.text(Analyst1_Pseud_settle_300[[5]],Analyst2_Pseud_settle_300[[5]],sig.level=0.95)
blandr.draw(Analyst1_Pseud_settle_300[[5]],Analyst2_Pseud_settle_300[[5]])
blandr.plot.normality(A1_A2blandr_300)
```

**2) Analyst 1 compared to Biospot:**


1 cfu

```{r, eval=TRUE}
A1_Biospot_sum_stats_Pseud_1<-blandr.output.text(Analyst1_Pseud_settle_1[[5]],Biospot_Pseud_settle_1[[5]],sig.level=0.95)
blandr.draw(Analyst1_Pseud_settle_1[[5]],Biospot_Pseud_settle_1[[5]])
blandr.plot.normality(A1_Biospotblandr_1)

```

10 cfu

```{r, eval=TRUE}
A1_Biospot_sum_stats_Pseud_10<-blandr.output.text(Analyst1_Pseud_settle_10[[5]],Biospot_Pseud_settle_10[[5]],sig.level=0.95)
blandr.draw(Analyst1_Pseud_settle_10[[5]],Biospot_Pseud_settle_10[[5]])
blandr.plot.normality(A1_Biospotblandr_10)

```

50 cfu

```{r, eval=TRUE}
A1_Biospot_sum_stats_Pseud_50<-blandr.output.text(Analyst1_Pseud_settle_50[[5]],Biospot_Pseud_settle_50[[5]],sig.level=0.95)
blandr.draw(Analyst1_Pseud_settle_50[[5]],Biospot_Pseud_settle_50[[5]])
blandr.plot.normality(A1_Biospotblandr_10)

```

100 cfu

```{r, eval=TRUE}
A1_Biospot_sum_stats_Pseud_100<-blandr.output.text(Analyst1_Pseud_settle_100[[5]],Biospot_Pseud_settle_100[[5]],sig.level=0.95)
blandr.draw(Analyst1_Pseud_settle_100[[5]],Biospot_Pseud_settle_100[[5]])
blandr.plot.normality(A1_Biospotblandr_100)

```
 
300 cfu 

```{r, eval=TRUE}
A1_Biospot_sum_stats_Pseud_300<-blandr.output.text(Analyst1_Pseud_settle_300[[5]],Biospot_Pseud_settle_300[[5]],sig.level=0.95)
blandr.draw(Analyst1_Pseud_settle_300[[5]],Biospot_Pseud_settle_300[[5]])
blandr.plot.normality(A1_Biospotblandr_300)

```

**3) Analyst 1 compared to AutoCol:**

1 cfu

```{r, eval=TRUE}
A1_AutoColsum_stats_Pseud_1<-blandr.output.text(Analyst1_Pseud_settle_1[[5]],AutoCol_Pseud_settle_1[[5]],sig.level=0.95)
blandr.draw(Analyst1_Pseud_settle_1[[5]],AutoCol_Pseud_settle_1[[5]])
blandr.plot.normality(A1_AutoColblandr_1)

```

10 cfu

```{r, eval=TRUE}
A1_AutoColsum_stats_Pseud_10<-blandr.output.text(Analyst1_Pseud_settle_10[[5]],AutoCol_Pseud_settle_10[[5]],sig.level=0.95)
blandr.draw(Analyst1_Pseud_settle_10[[5]],AutoCol_Pseud_settle_10[[5]])
blandr.plot.normality(A1_AutoColblandr_10)

```

50 cfu

```{r, eval=TRUE}
A1_AutoColsum_stats_Pseud_50<-blandr.output.text(Analyst1_Pseud_settle_50[[5]],AutoCol_Pseud_settle_50[[5]],sig.level=0.95)
blandr.draw(Analyst1_Pseud_settle_50[[5]],Analyst1_Pseud_settle_50[[5]])
blandr.plot.normality(A1_AutoColblandr_10)

```

100 cfu

```{r, eval=TRUE}
A1_AutoColsum_stats_Pseud_100<-blandr.output.text(Analyst1_Pseud_settle_100[[5]],AutoCol_Pseud_settle_100[[5]],sig.level=0.95)
blandr.draw(Analyst1_Pseud_settle_100[[5]],AutoCol_Pseud_settle_100[[5]])
blandr.plot.normality(A1_AutoColblandr_100)

```
 
300 cfu 

```{r, eval=TRUE}
A1_AutoColsum_stats_Pseud_300<-blandr.output.text(Analyst1_Pseud_settle_300[[5]],AutoCol_Pseud_settle_300[[5]],sig.level=0.95)
blandr.draw(Analyst1_Pseud_settle_300[[5]],AutoCol_Pseud_settle_300[[5]])
blandr.plot.normality(A1_AutoColblandr_300)

```

**4) Analyst 2 compared to Biospot:**


1 cfu

```{r, eval=TRUE}
A2_Biospot_sum_stats_Pseud_1<-blandr.output.text(Analyst2_Pseud_settle_1[[5]],Biospot_Pseud_settle_1[[5]],sig.level=0.95)
blandr.draw(Analyst2_Pseud_settle_1[[5]],Biospot_Pseud_settle_1[[5]])
blandr.plot.normality(A2_Biospotblandr_1)

```

10 cfu

```{r, eval=TRUE}
A2_Biospot_sum_stats_Pseud_10<-blandr.output.text(Analyst2_Pseud_settle_10[[5]],Biospot_Pseud_settle_10[[5]],sig.level=0.95)
blandr.draw(Analyst2_Pseud_settle_10[[5]],Biospot_Pseud_settle_10[[5]])
blandr.plot.normality(A2_Biospotblandr_10)

```

50 cfu

```{r, eval=TRUE}
A2_Biospot_sum_stats_Pseud_50<-blandr.output.text(Analyst2_Pseud_settle_50[[5]],Biospot_Pseud_settle_50[[5]],sig.level=0.95)
blandr.draw(Analyst2_Pseud_settle_50[[5]],Biospot_Pseud_settle_50[[5]])
blandr.plot.normality(A2_Biospotblandr_10)

```

100 cfu

```{r, eval=TRUE}
A2_Biospot_sum_stats_Pseud_100<-blandr.output.text(Analyst2_Pseud_settle_100[[5]],Biospot_Pseud_settle_100[[5]],sig.level=0.95)
blandr.draw(Analyst2_Pseud_settle_100[[5]],Biospot_Pseud_settle_100[[5]])
blandr.plot.normality(A2_Biospotblandr_100)

```
 
300cfu 

```{r, eval=TRUE}
A2_Biospot_sum_stats_Pseud_300<-blandr.output.text(Analyst2_Pseud_settle_300[[5]],Biospot_Pseud_settle_300[[5]],sig.level=0.95)
blandr.draw(Analyst2_Pseud_settle_300[[5]],Biospot_Pseud_settle_300[[5]])
blandr.plot.normality(A2_Biospotblandr_300)

```

**5) Analyst 2 compared to AutoCol: **

1 cfu

```{r, eval=TRUE}
A2_AutoColsum_stats_Pseud_1<-blandr.output.text(Analyst2_Pseud_settle_1[[5]],AutoCol_Pseud_settle_1[[5]],sig.level=0.95)
blandr.draw(Analyst2_Pseud_settle_1[[5]],AutoCol_Pseud_settle_1[[5]])
blandr.plot.normality(A2_AutoColblandr_1)

```

10 cfu

```{r, eval=TRUE}
A2_AutoColsum_stats_Pseud_10<-blandr.output.text(Analyst2_Pseud_settle_10[[5]],AutoCol_Pseud_settle_10[[5]],sig.level=0.95)
blandr.draw(Analyst2_Pseud_settle_10[[5]],AutoCol_Pseud_settle_10[[5]])
blandr.plot.normality(A2_AutoColblandr_10)

```

50 cfu

```{r, eval=TRUE}
A2_AutoColsum_stats_Pseud_50<-blandr.output.text(Analyst2_Pseud_settle_50[[5]],AutoCol_Pseud_settle_50[[5]],sig.level=0.95)
blandr.draw(Analyst2_Pseud_settle_50[[5]],Analyst1_Pseud_settle_50[[5]])
blandr.plot.normality(A2_AutoColblandr_10)

```

100 cfu

```{r, eval=TRUE}
A2_AutoColsum_stats_Pseud_100<-blandr.output.text(Analyst2_Pseud_settle_100[[5]],AutoCol_Pseud_settle_100[[5]],sig.level=0.95)
blandr.draw(Analyst2_Pseud_settle_100[[5]],AutoCol_Pseud_settle_100[[5]])
blandr.plot.normality(A2_AutoColblandr_100)

```
 
300cfu

```{r, eval=TRUE}
A2_AutoColsum_stats_Pseud_300<-blandr.output.text(Analyst2_Pseud_settle_300[[5]],AutoCol_Pseud_settle_300[[5]],sig.level=0.95)
blandr.draw(Analyst2_Pseud_settle_300[[5]],AutoCol_Pseud_settle_300[[5]])
blandr.plot.normality(A2_AutoColblandr_300)
```

**6) Biospot compared to AutoCol :**

1 cfu

```{r, eval=TRUE}
Biospot_AutoColsum_stats_Pseud_1<-blandr.output.text(Biospot_Pseud_settle_1[[5]],AutoCol_Pseud_settle_1[[5]],sig.level=0.95)
blandr.draw(Biospot_Pseud_settle_1[[5]],AutoCol_Pseud_settle_1[[5]])
blandr.plot.normality(Biospot_AutoColblandr_1)

```

10 cfu

```{r, eval=TRUE}
Biospot_AutoColsum_stats_Pseud_10<-blandr.output.text(Biospot_Pseud_settle_10[[5]],AutoCol_Pseud_settle_10[[5]],sig.level=0.95)
blandr.draw(Biospot_Pseud_settle_10[[5]],AutoCol_Pseud_settle_10[[5]])
blandr.plot.normality(Biospot_AutoColblandr_10)

```

50 cfu

```{r, eval=TRUE}
Biospot_AutoColsum_stats_Pseud_50<-blandr.output.text(Biospot_Pseud_settle_50[[5]],AutoCol_Pseud_settle_50[[5]],sig.level=0.95)
blandr.draw(Biospot_Pseud_settle_50[[5]],Analyst1_Pseud_settle_50[[5]])
blandr.plot.normality(Biospot_AutoColblandr_10)

```

100 cfu

```{r, eval=TRUE}
Biospot_AutoColsum_stats_Pseud_100<-blandr.output.text(Biospot_Pseud_settle_100[[5]],AutoCol_Pseud_settle_100[[5]],sig.level=0.95)
blandr.draw(Biospot_Pseud_settle_100[[5]],AutoCol_Pseud_settle_100[[5]])
blandr.plot.normality(Biospot_AutoColblandr_100)

```
 
300 cfu

```{r, eval=TRUE}
Biospot_AutoColsum_stats_Pseud_300<-blandr.output.text(Biospot_Pseud_settle_300[[5]],AutoCol_Pseud_settle_300[[5]],sig.level=0.95)
blandr.draw(Biospot_Pseud_settle_300[[5]],AutoCol_Pseud_settle_300[[5]])
blandr.plot.normality(Biospot_AutoColblandr_300)
```

