# Experiment 2

## Procedure

This arm of the study involves setting down 50 contact plates and 50 settle plates in different lab locations. Performed on three days giving a total of 300 plates. This study will give a representative set of EM plates containing environmental isolates. 

The contact plates and settle plates will be incubated at 30-35°C for 5 days. 

Once the incubation period is complete, the plates will be read by two technicians - without marking with a pen and by both plate readers. 


```{r, include=FALSE}
library(blandr)
library(tidyverse)
library(xlsx)
```


```{r,include=FALSE,resuls="hide"}
setwd("/Users/krpl818/OneDrive - AZCollaboration/Documents/Plate reader project")

library(readxl)
experiment_2 <- read_excel("Experiment tables.xlsx", sheet=2,
                                col_types = c("text", "text", "text","numeric","numeric"))
experiment_2<-as_tibble(experiment_2)
attach(experiment_2)
names(experiment_2)
```

```{r,results="hide"}

Analyst1_day1_settle_1<-filter(experiment_2, experiment_2["Method"]=="First Analyst",experiment_2["Day"]=="Day 1'",experiment_2["Plate Type"]=='Settle')

Analyst1_day2_settle_1<-filter(experiment_2, experiment_2["Method"]=="First Analyst",experiment_2["Day"]=="Day 2'",experiment_2["Plate Type"]=='Settle')

Analyst1_day3_settle_1<-filter(experiment_2, experiment_2["Method"]=="First Analyst",experiment_2["Day"]=="Day 3'",experiment_2["Plate Type"]=='Settle')

Analyst2_day1_settle_1<-filter(experiment_2, experiment_2["Method"]=="Second Analyst",experiment_2["Day"]=="Day 1'",experiment_2["Plate Type"]=='Settle')

Analyst2_day2_settle_1<-filter(experiment_2, experiment_2["Method"]=="Second Analyst",experiment_2["Day"]=="Day 2'",experiment_2["Plate Type"]=='Settle')

Analyst2_day3_settle_1<-filter(experiment_2, experiment_2["Method"]=="Second Analyst",experiment_2["Day"]=="Day 3'",experiment_2["Plate Type"]=='Settle')

Biospot_day1_settle_1<-filter(experiment_2, experiment_2["Method"]=="Biospot",experiment_2["Day"]=="Day 1'",experiment_2["Plate Type"]=='Settle')

Biospot_day2_settle_1<-filter(experiment_2, experiment_2["Method"]=="Biospot",experiment_2["Day"]=="Day 2'",experiment_2["Plate Type"]=='Settle')

Biospot_day3_settle_1<-filter(experiment_2, experiment_2["Method"]=="Biospot",experiment_2["Day"]=="Day 3'",experiment_2["Plate Type"]=='Settle')

Analyst1_day1_contact_1<-filter(experiment_2, experiment_2["Method"]=="First Analyst",experiment_2["Day"]=="Day 1'",experiment_2["Plate Type"]=='Contact')

Analyst1_day2_contact_1<-filter(experiment_2, experiment_2["Method"]=="First Analyst",experiment_2["Day"]=="Day 2'",experiment_2["Plate Type"]=='Contact')

Analyst1_day3_contact_1<-filter(experiment_2, experiment_2["Method"]=="First Analyst",experiment_2["Day"]=="Day 3'",experiment_2["Plate Type"]=='Contact')

Analyst2_day1_contact_1<-filter(experiment_2, experiment_2["Method"]=="Second Analyst",experiment_2["Day"]=="Day 1'",experiment_2["Plate Type"]=='Contact')

Analyst2_day2_contact_1<-filter(experiment_2, experiment_2["Method"]=="Second Analyst",experiment_2["Day"]=="Day 2'",experiment_2["Plate Type"]=='Contact')

Analyst2_day3_contact_1<-filter(experiment_2, experiment_2["Method"]=="Second Analyst",experiment_2["Day"]=="Day 3'",experiment_2["Plate Type"]=='Contact')

Biospot_day1_contact_1<-filter(experiment_2, experiment_2["Method"]=="Biospot",experiment_2["Day"]=="Day 1'",experiment_2["Plate Type"]=='Contact')

Biospot_day2_contact_1<-filter(experiment_2, experiment_2["Method"]=="Biospot",experiment_2["Day"]=="Day 2'",experiment_2["Plate Type"]=='Contact')

Biospot_day3_contact_1<-filter(experiment_2, experiment_2["Method"]=="Biospot",experiment_2["Day"]=="Day 3'",experiment_2["Plate Type"]=='Contact')

```

```{r, results="hide"}
experiment_2_settle<-filter(experiment_2,experiment_2["Plate Type"]=='Settle')

experiment_2_settle<-as.data.frame(experiment_2_settle)

experiment_2_contact<-filter(experiment_2,experiment_2["Plate Type"]=='Contact')

experiment_2_contact<-as.data.frame(experiment_2_contact)
```

## Settle Plates

```{r, eval=TRUE}
ggplot(data = experiment_2_settle,aes(x=experiment_2_settle$Method, y=experiment_2_settle$`Number of colonies`))+
  geom_point(aes(x=experiment_2_settle$Method, y=experiment_2_settle$`Number of colonies`,color=experiment_2_settle$Method))+facet_wrap(~experiment_2_settle$Day)+
  geom_line(aes(group=interaction(experiment_2_settle$Day,experiment_2_settle$Repeat)),color='black')+
  labs(y="Number of Colonies counted", x = "Method")+theme(legend.position = "none")
```



```{r,results="hide"}
#settle

Analyst1_Analyst2_settle_1<-blandr.statistics(Analyst1_day1_settle_1[[4]],Analyst2_day1_settle_1[[4]],sig.level=0.95)

Analyst1_Analyst2_settle_2<-blandr.statistics(Analyst1_day2_settle_1[[4]],Analyst2_day2_settle_1[[4]],sig.level=0.95)

Analyst1_Analyst2_settle_3<-blandr.statistics(Analyst1_day3_settle_1[[4]],Analyst2_day3_settle_1[[4]],sig.level=0.95)

Analyst1_Biospot_settle_1<-blandr.statistics(Analyst1_day1_settle_1[[4]],Biospot_day1_settle_1[[4]],sig.level=0.95)

Analyst1_Biospot_settle_2<-blandr.statistics(Analyst1_day2_settle_1[[4]],Biospot_day2_settle_1[[4]],sig.level=0.95)

Analyst1_Biospot_settle_3<-blandr.statistics(Analyst1_day3_settle_1[[4]],Biospot_day3_settle_1[[4]],sig.level=0.95)

Analyst2_Biospot_settle_1<-blandr.statistics(Analyst2_day1_settle_1[[4]],Biospot_day1_settle_1[[4]],sig.level=0.95)

Analyst2_Biospot_settle_2<-blandr.statistics(Analyst2_day2_settle_1[[4]],Biospot_day2_settle_1[[4]],sig.level=0.95)

Analyst2_Biospot_settle_3<-blandr.statistics(Analyst2_day3_settle_1[[4]],Biospot_day3_settle_1[[4]],sig.level=0.95)

#contact

Analyst1_Analyst2_contact_1<-blandr.statistics(Analyst1_day1_contact_1[[4]],Analyst2_day1_contact_1[[4]],sig.level=0.95)

Analyst1_Analyst2_contact_2<-blandr.statistics(Analyst1_day2_contact_1[[4]],Analyst2_day2_contact_1[[4]],sig.level=0.95)

Analyst1_Analyst2_contact_3<-blandr.statistics(Analyst1_day3_contact_1[[4]],Analyst2_day3_contact_1[[4]],sig.level=0.95)

Analyst1_Biospot_contact_1<-blandr.statistics(Analyst1_day1_contact_1[[4]],Biospot_day1_contact_1[[4]],sig.level=0.95)

Analyst1_Biospot_contact_2<-blandr.statistics(Analyst1_day2_contact_1[[4]],Biospot_day2_contact_1[[4]],sig.level=0.95)

Analyst1_Biospot_contact_3<-blandr.statistics(Analyst1_day3_contact_1[[4]],Biospot_day3_contact_1[[4]],sig.level=0.95)

Analyst2_Biospot_contact_1<-blandr.statistics(Analyst2_day1_contact_1[[4]],Biospot_day1_contact_1[[4]],sig.level=0.95)

Analyst2_Biospot_contact_2<-blandr.statistics(Analyst2_day2_contact_1[[4]],Biospot_day2_contact_1[[4]],sig.level=0.95)

Analyst2_Biospot_contact_3<-blandr.statistics(Analyst2_day3_contact_1[[4]],Biospot_day3_contact_1[[4]],sig.level=0.95)

```


**Analyst 1 vs Analyst 2**

Day 1

```{r, eval=TRUE}
Analyst1_Analyst2_settle1_stats<-blandr.output.text(Analyst1_day1_settle_1[[4]],Analyst2_day1_settle_1[[4]],sig.level=0.95)
blandr.draw(Analyst1_day1_settle_1[[4]],Analyst2_day1_settle_1[[4]])
blandr.plot.normality(Analyst1_Analyst2_settle_1)

```

Day 2

```{r, eval=TRUE}
Analyst1_Analyst2_settle2_stats<-blandr.output.text(Analyst1_day2_settle_1[[4]],Analyst2_day2_settle_1[[4]],sig.level=0.95)
blandr.draw(Analyst1_day2_settle_1[[4]],Analyst2_day2_settle_1[[4]])
blandr.plot.normality(Analyst1_Analyst2_settle_2)

```

Day 3

```{r, eval=TRUE}
Analyst1_Analyst2_settle3_stats<-blandr.output.text(Analyst1_day3_settle_1[[4]],Analyst2_day3_settle_1[[4]],sig.level=0.95)
blandr.draw(Analyst1_day3_settle_1[[4]],Analyst2_day3_settle_1[[4]])
blandr.plot.normality(Analyst1_Analyst2_settle_3)

```

**Analyst 1 vs Biospot**

Day 1

```{r, eval=TRUE}
Analyst1_Biospot_settle1_stats<-blandr.output.text(Analyst1_day1_settle_1[[4]],Biospot_day1_settle_1[[4]],sig.level=0.95)
blandr.draw(Analyst1_day1_settle_1[[4]],Biospot_day1_settle_1[[4]])
blandr.plot.normality(Analyst1_Biospot_settle_1)

```

Day 2

```{r, eval=TRUE}
Analyst1_Biospot_settle2_stats<-blandr.output.text(Analyst1_day2_settle_1[[4]],Biospot_day2_settle_1[[4]],sig.level=0.95)
blandr.draw(Analyst1_day2_settle_1[[4]],Biospot_day2_settle_1[[4]])
blandr.plot.normality(Analyst1_Biospot_settle_2)

```

Day 3

```{r, eval=TRUE}
Analyst1_Biospot_settle3_stats<-blandr.output.text(Analyst1_day3_settle_1[[4]],Biospot_day3_settle_1[[4]],sig.level=0.95)
blandr.draw(Analyst1_day3_settle_1[[4]],Biospot_day3_settle_1[[4]])
blandr.plot.normality(Analyst1_Biospot_settle_3)

```

**Analyst 2 vs Biospot**

Day 1

```{r, eval=TRUE}
Analyst2_Biospot_settle1_stats<-blandr.output.text(Analyst2_day1_contact_1[[4]],Biospot_day1_contact_1[[4]],sig.level=0.95)
blandr.draw(Analyst2_day1_contact_1[[4]],Biospot_day1_contact_1[[4]])
blandr.plot.normality(Analyst2_Biospot_contact_1)

```

Day 2

```{r, eval=TRUE}
Analyst2_Biospot_settle2_stats<-blandr.output.text(Analyst2_day2_settle_1[[4]],Biospot_day2_settle_1[[4]],sig.level=0.95)
blandr.draw(Analyst2_day2_settle_1[[4]],Biospot_day2_settle_1[[4]])
blandr.plot.normality(Analyst2_Biospot_settle_2)

```

Day 3

```{r, eval=TRUE}
Analyst2_Biospot_settle3_stats<-blandr.output.text(Analyst2_day3_settle_1[[4]],Biospot_day3_settle_1[[4]],sig.level=0.95)
blandr.draw(Analyst1_day2_settle_1[[4]],Biospot_day3_settle_1[[4]])
blandr.plot.normality(Analyst2_Biospot_settle_3)

```

## Contact Plates 

```{r, eval=TRUE}
ggplot(data = experiment_2_contact,aes(x=experiment_2_contact$Method, y=experiment_2_contact$`Number of colonies`))+
  geom_point(aes(x=experiment_2_contact$Method, y=experiment_2_contact$`Number of colonies`,color=experiment_2_contact$Method))+facet_wrap(~experiment_2_contact$Day)+
  geom_line(aes(group=interaction(experiment_2_contact$Day,experiment_2_contact$Repeat)),color='black')+
  labs(y="Number of Colonies counted", x = "Method")+theme(legend.position = "none")
```

**Analyst 1 vs Analyst 2**

Day 1

```{r, eval=TRUE}
Analyst1_Analyst2_contact1_stats<-blandr.output.text(Analyst1_day1_contact_1[[4]],Analyst2_day1_contact_1[[4]],sig.level=0.95)
blandr.draw(Analyst1_day1_contact_1[[4]],Analyst2_day1_contact_1[[4]])
blandr.plot.normality(Analyst1_Analyst2_contact_1)

```

Day 2

```{r, eval=TRUE}
Analyst1_Analyst2_contact2_stats<-blandr.output.text(Analyst1_day2_contact_1[[4]],Analyst2_day2_contact_1[[4]],sig.level=0.95)
blandr.draw(Analyst1_day2_contact_1[[4]],Analyst2_day2_contact_1[[4]])
blandr.plot.normality(Analyst1_Analyst2_contact_2)

```

Day 3

```{r, eval=TRUE}
Analyst1_Analyst2_contact3_stats<-blandr.output.text(Analyst1_day3_contact_1[[4]],Analyst2_day3_contact_1[[4]],sig.level=0.95)
blandr.draw(Analyst1_day3_contact_1[[4]],Analyst2_day3_contact_1[[4]])
blandr.plot.normality(Analyst1_Analyst2_contact_3)

```

**Analyst 1 vs Biospot**

Day 1

```{r, eval=TRUE}
Analyst1_Biospot_contact2_stats<-blandr.output.text(Analyst1_day1_contact_1[[4]],Biospot_day1_contact_1[[4]],sig.level=0.95)
blandr.draw(Analyst1_day1_contact_1[[4]],Biospot_day1_contact_1[[4]])
blandr.plot.normality(Analyst1_Biospot_contact_1)

```

Day 2

```{r, eval=TRUE}
Analyst1_Biospot_contact2_stats<-blandr.output.text(Analyst1_day2_contact_1[[4]],Biospot_day2_contact_1[[4]],sig.level=0.95)
blandr.draw(Analyst1_day2_contact_1[[4]],Biospot_day2_contact_1[[4]])
blandr.plot.normality(Analyst1_Biospot_contact_2)

```

Day 3

```{r, eval=TRUE}
Analyst1_Biospot_contact3_stats<-blandr.output.text(Analyst1_day3_contact_1[[4]],Biospot_day3_contact_1[[4]],sig.level=0.95)
blandr.draw(Analyst1_day3_contact_1[[4]],Biospot_day3_contact_1[[4]])
blandr.plot.normality(Analyst1_Biospot_contact_3)

```

**Analyst 2 vs Biospot**

Day 1

```{r, eval=TRUE}
Analyst2_Biospot_contact1_stats<-blandr.output.text(Analyst2_day1_contact_1[[4]],Biospot_day1_contact_1[[4]],sig.level=0.95)
blandr.draw(Analyst2_day1_contact_1[[4]],Biospot_day1_contact_1[[4]])
blandr.plot.normality(Analyst2_Biospot_contact_1)

```

Day 2

```{r, eval=TRUE}
Analyst2_Biospot_contact2_stats<-blandr.output.text(Analyst2_day2_contact_1[[4]],Biospot_day2_contact_1[[4]],sig.level=0.95)
blandr.draw(Analyst2_day2_contact_1[[4]],Biospot_day2_contact_1[[4]])
blandr.plot.normality(Analyst2_Biospot_contact_2)

```

Day 3

```{r, eval=TRUE}
Analyst2_Biospot_contact3_stats<-blandr.output.text(Analyst2_day3_contact_1[[4]],Biospot_day3_contact_1[[4]],sig.level=0.95)
blandr.draw(Analyst1_day2_contact_1[[4]],Biospot_day3_contact_1[[4]])
blandr.plot.normality(Analyst2_Biospot_contact_3)

```
